% File Name: Muhammad_Taqui_Example.tex
% Author: Muhammad Taqui
% Date: 22 June 2022

\documentclass{article}

\begin{document}

\title{Example LaTeX Document}
\author{Muhammad Taqui}
\date{\today}
\maketitle

\section{\textbf{\textit{\underline{Introduction}}}}

This is the introduction section of the document. Here, we demonstrate the use of bold, italic, and underlined text within a LaTeX document.

\subsection{\textbf{\textit{\underline{Purpose}}}}

The purpose of this document is to showcase various formatting options available in LaTeX, such as bold, italic, and underlined text.

\subsection{\textbf{\textit{\underline{Scope}}}}

The scope of this document is limited to demonstrating basic LaTeX formatting features.

\section{\textbf{\textit{\underline{Methodology}}}}

In this section, we describe the methodology used to create this document. We start with defining the document class as \texttt{article} and then include necessary packages for text formatting.

\subsection{\textbf{\textit{\underline{Document Class}}}}

The document class used for this document is \texttt{article}, which is suitable for short documents like reports, articles, or papers.

\subsection{\textbf{\textit{\underline{Packages}}}}

We include the \texttt{amsmath} package for mathematical typesetting and the \texttt{graphicx} package for including images in the document.

\section{\textbf{\textit{\underline{Conclusion}}}}

This document demonstrates the use of bold, italic, and underlined text, as well as numbering for sections and subsections in LaTeX.


\end{document}
